\section{Introduction}
\label{sect:intro}

Communication networks nowadays have greatly improved the connectivity of the world. This connectivity
inspires and leads to a variety of online and real-time applications, like voice over IP (VoIP), video
streaming, online interactive gaming, video conferencing, etc. These applications impose diverse Quality
of Service (QoS) requirements on latency, bandwidth, jitter and error-rate. On the other hand, the
underlying networks can not provide unlimited bandwidth. According to~\cite{akamai}, the average
connection speed in the United States is 14.2Mbps. When users use multiple applications at the same time,
these applications compete for the relatively scarce bandwidth, thus leading to degradations of overall
performance.

A common approach to this problem is to prioritize applications' traffic flows so that QoS of high
priority applications can be effectively enforced. To this end, many QoS mechanisms have been proposed and
implemented (\todo{citations see flowQoS paper}). Nonetheless, these mechanisms have not been deployed in small scale broadband
access networks (e.g., home networks), for several reasons. First, many home routers have limited memory and
computation resources. Therefore, they may not be able to process and enforce complicated QoS policies
"on-the-fly"~\cite{But_Comm2018}. Second, users' demands of QoS for different applications may change in different
scenarios. For example, in a home network setting, a user may demand high definition (HD) quality of videos while
no one is playing online video games. When other users are playing online video games, she is willing to accept
standard definition (SD) quality of videos. However, many home users do not have knowledge to configure the
underlying networks to meet their needs.

Recently Software Defined Networking (SDN) has emerged as a promising approach for providing flexible network
programmability. SDN proposes to decouple the control plane from the data plane, and therefore it leaves the
existing routers and switches as simple forwarding devices. The control logic is centralized and deployed on a
server, called SDN controller, which facilitates dynamic configuration, operation and monitoring of a network.
\todo{More contents can be added here.}

In this paper, we present QoSManager, a configurable and adaptive QoS management framework based on SDN. In
QosManger, users specify high-level QoS policies (e.g., minimum bandwidth, recommended bandwidth and priority)
for different types of traffic, and QoSManager controller will dynamically assign each flow to a queue with an
appropriate sending rate to maximize the QoS utility function (\refsect{qosUF}) under the limited link capacity.
QoSManger provides an interface for modifying QoS policies at runtime (configurable) and recompute the assignments
of flows to queues when flow is added to or removed from the network (adaptive).

This paper presents several contributions. First, we design the specification language,  we take into account
that the QoS requirement for an application may change in different scenarios. Second, we design and implement
QoSManager, a configurable and adaptive QoS management framework using SDN support. Especially, we propose a novel
algorithm to assign flows to queues with appropriate rates to effectively enforce QoS. Third, we demonstrate the
effectiveness of QosManager by emulating different network scenarios.

The rest of the paper proceeds as follows. 
\refsect{related} presents related work in QoS, as well as SDN-based solutions
for home and broadband access networks. 
\refsect{qosmanager} describes the design of our system, as well as its implementation using Ryu and Open vSwitch.
\refsect{experiment} evaluates
our system in the
context of competing flows. \refsect{future} discusses future work
and concludes.
